On pulsed microwave acoustic resonant viral inactivation: summary

### 2020-07-24 documents/pamphlet.tex
Eppenwolf milled out

\title{Maxwell's Silver Hammer, summarized:\\ On the application of pulsed microwave acoustic resonant viral inactivation}

@@

This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Assign blame to Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}

@@

The literature is littered with irreproducible claims of non-thermal effects; however, this certainly appears to be a singular anomaly.

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.

@@

By extending this work into the time-domain, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits. Better yet, by scanning the focal point or beam , a significant area can be treated with a relatively small output power.

\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this

@@

It penetrates tissue.

@@

Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement. We provide a reference design that costs \$3 in prototype quantities.

@@

>>>>

\title{On pulsed microwave acoustic resonant viral inactivation: summary}

@@

This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}

@@

The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass distribution, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.

@@

\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.

This work can be extended with the following assertion: the virus' Q factor is only 2, meaning that the steady-state amplitude should be reached in some nanoseconds.

Barring protein mechanical fatigue [] or other mechanisms that could prolong the inactivation duration, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits. Better yet, by scanning the focal point, a significant area can be treated with a relatively small transmit power.

\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this is may be transferable.

@@

It produces no ozone and causes no damage to tissue (unlike near UV) even during continuous exposure, penetrates tissue (unlike far UV and cold-plasma), and

@@

If this is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized.

This is not a particularly demanding requirement.

We provide a reference design that costs \$3 in prototype quantities.

@@

{\Large \textbf{Tasks}}

We can see the following

\begin{itemize}
	\item To prevent duplication of work, are any other teams working on this now? It seems a rather obvious technique. A thorough review of arxiv etc should be performed.
	\item Double-check all figures and assumptions.
	\item Get permission to use York University as affiliation, post on arxiv.
	\item Send off spectrometer (or, ideally, a more precise piece of equipment) to a BSL with a sample of NCoV to obtain the spectra and thresholds.
	\item Determine the ideal application (requires detailed sims), finish the design for the electromagnetic mask, start bronchoscopic trials?

	\item Check with the FCC/Industry Canada if we can get a temporary exemption for these intentional radiators?

\end{itemize}
